---
title: "FormingTheCommunity"
author: "NHI"
date: "May 28, 2018"
output: word_document
params: 
  n: NA
---

#Forming the Community
####Goal: Participants develop familiiarty with each other, build a strong sense of unity, and common purpose, and a willingness to be active participants in the various learning experiences of the LDZ.

##OFFICIAL WELCOME
####Info: MC is a staff member, chosen by ED's

MC: Welcome DELEGATES to the 2018 - NATIONAL - Lorenzo de Zavala - Youth - Legislative - Session!!!!!!!!!!

MC: We will now begin our official roll call! Who is here from:
```{r, echo=FALSE}
params$n

```

MC: Thank you all for being with us, we will now continue with our program. I would now like to welcome to the stage, Education Director: 
```{r}
params$n
```

I would now like to welcome to the stage, Education Director: 
```{r}
params$n

```

I would now like to welcome to the stage, Education Director: 
```{r}
params$n
```

I would now like to welcome to the stage, Education Director: 
```{r}
```