---
title: "FormingTheCommunity"
author: "NHI"
date: "May 24, 2018"
output: word_document
params: 
  n: NA
  data: NA
  test: NA
  test2: NA
---

#Forming the Community
Goal: Participants develop familiiarty with each other, build a strong sense of unity, and common purpose, and a willingness to be active participants in the various learning experiences of the LDZ.

##OFFICIAL WELCOME
(DELIVERED BY A STAFF MEMBER - Called the MC)

[With Emphasis] Welcome DELEGATES to the 2018…NATIONAL…Lorenzo de Zavala…Youth…Legislative…Session…

We will now begin the official roll call. Who is here from…
```{r, echo=FALSE}

```

Thank you all for being with us, we will continue with our program

I would now like to welcome to the stage, Education Director: 
```{r}
params$n
```

I would now like to welcome to the stage, Education Director: 
```{r}
params$data
```

I would now like to welcome to the stage, Education Director: 
```{r}
params$test
```

I would now like to welcome to the stage, Education Director: 
```{r}
params$test2
```