---
title: "FormingTheCommunity"
author: "National Lorenzo de Zavala Youth Legislative Session"
date: "May 31, 2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#Variable needed for program
mc <- "MC"
year <- "year"
program <- "program"
location_table <- "table"
ed1 <- "ed1"
staff_list <- "long list"
staff1 <- "staff1"
staff2 <- "staff 2"
staffhigh <- "highest staff"
ed2 <- "ed2"
```

# OBJECTIVE
Participants develop familiarity with each other, build a strong sense of unity and common purpose, and a willingness to be active participants in the various learning experiences of the LDZ. 

# PROGRAM
## OFFICIAL WELCOME: 

```{r, echo=FALSE}
sprintf("DELIVERED BY A STAFF MEMBER: %s", mc)
```

```{r, echo=FALSE}
sprintf("%s»: [With Emphasis] Welcome DELEGATES to the %s %s Lorenzo de Zavala...Youth...Legislative... Session...", mc, year, program)
```

```{r, echo=FALSE}
sprintf("%s: [Wait for cheers in between each state/ country] We will now begin the official roll call. Who is here from...",mc)
```

```{r, echo=FALSE}
location_table
```

```{r, echo=FALSE}
sprintf("%s: Thank you all for being with us and we will continue with our program. I would now like to welcome to the stage, your Education Director, %s for opening remarks", mc, ed1)
```

## ED WELCOME: 
Ed gives welcome speech
```{r, echo=FALSE}
sprintf("%s: Thank you all again! I would like to welcome back to the stage, your MC %s", ed1, mc)
```

##STAFF INTRODUCTIONS
```{r, echo=FALSE}
sprintf("%s: I would like to now introduce the %s %s Lorenzo de Zavala Youth Legislative Session Staff to the stage:", mc, year, program)
```

```{r, echo=FALSE}
staff_list
```

##STAFF TESTIMONIALS
```{r, echo=FALSE}
sprintf("%s: Please give a hand for your staff! ", mc)

sprintf("%s: would like to welcome to podium %s and %s to give staff testimonials and challenges for the delegation.",mc, staff1, staff2)

```

##NHI OATH
```{r, echo=FALSE}
sprintf("%s: Thank you to our two staff speakers!", mc)

sprintf("%s: I would like to introduce the highest-ranking Staff member, %s back to the podium to lead us in the NHI oath.", mc, staffhigh)
```

###OATH
- I, SAY YOUR NAME, [actually say the words “SAY YOUR NAME” so the students will say their name]
- pledge that this weekend 
- I will take on the title of community partner, investor, and NHI member. 
- Therefore, I will commit to nothing but excellence. 
- I will exhibit the behaviors of a professional
- that reflect the ethics of my community. 
- I know that my peers are not my competitors
- or rivals 
- but rather my biggest collaborators 
- and heirs to grow with me. 
- I will abide by all the rules and regulations 
- and respect the policies of the National Hispanic Institute 
- as I will reflect the core family values instilled me generations ago. 
- I will push myself to be the best version of myself
- and will exhibit a pride in my character 
- and integrity that demonstrates
- the deep lessons of my family and community. 
- This is I swear. 
- I am ready to begin.


##NHI OATH
```{r, echo=FALSE}
sprintf("%s: I now welcome Education Director, %s, to the stage to share additional remarks", mc, ed2)
```
##ED OPENING MESSAGE 
-	Official institutional welcome 
-	History of the NHI partnership
-	History and mission of the university
-	Importance and why university partners with NHI
-	The importance of “Envisioning the Future”
-	Opportunities for higher education at host

##Remaining Programming
- Host introduction (as applicable)
- Social Interactive Activities (Circle Counter Circle, Values, Diversity, What did we learn)

###Optional other activities
-	History game that challenges students to explain the conditions in Europe that led to the establishment of the U.S. and different Latin American countries. (30 minutes)
-	Envision exercise in which students are challenged to imagine life in the world in the next 20, 30, and even 40 years from now. (30 minutes)
-	Show and tell exercise where samples of proposals are selected and read to determine whether or not they meet the criterion for building and advancing societal/community life (asset view) (30 minutes)

